gij bent 2

### 2024-11-27 paper/paper.qmd
Further talk about bimodal distribution found in the coefficients

Note that each of the two different distributions might not consist of a homogeneous type of people. For example, the innovative corrections might include people in regions where the innovative form is rarely used, and who use the innovative form nonetheless. At the same time, innovative corrections might also stem from people in an already innovative area who "out-innovate" the expectations, using the innovative form even more often than is expected. We will attempt to build profiles of each correction direction later TODO.

@@

@fig-region-violin shows the dispersion of variation by Flemish dialect region. Here, we do not see a "reverse" pattern, in contrast to @fig-gender-violin.  There seem to be two variation profiles: a Brabant and a non-Brabant variation profile. The Brabant dialect shows individual variation which is comparable both for innovative and conservative variants. In the three non-Brabant regions, we see that there are some innovators, but they are generally few -- the dialects gravitate towards more conservative corrections.

>>>>

Note that each of the two different distributions might not consist of a homogeneous type of people. For example, the innovative corrections might include people in regions where the innovative form is rarely used, and who use the innovative form nonetheless. At the same time, innovative corrections might also stem from people in an already innovative area who "out-innovate" the expectations, using the innovative form even more often than is expected. We will attempt to tease out this distinction in the next section.

@@

@fig-region-violin shows the dispersion of variation by Flemish dialect region. Here, we do not see a "reverse" pattern, in contrast to @fig-gender-violin.  There seem to be two variation profiles: a Brabant variation profile, and a non-Brabant variation profile. The Brabant dialect shows a slight preference for innovation at the upper end of the coefficient values, with declining coefficents towards conserative corrections. In the three non-Brabant regions, we see that there are some innovators, but they are generally few. In these dialects, the values gravitate towards more conservative corrections. With these results, we have an explanation for the bi-modal nature of @fig-general-density: the first distribution, centred *below* zero, consists mostly of language users from non-Brabant dialect areas who are even more conservative than we expect from their region. The second distribution, centred *above* zero, consists mostly of eager innovators from the already innovative Brabant dialect area.
